О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 12

A bit more strong result can also be claimed.

@@

\begin{proof}
	Exploit Construction~\ref{con:planar_set_with_minimeter_1} to get $M'\in \mathfrak{M}(2,n-m+2)$
	with $M'_1, M'_2 \in M'$ and $|M'_1 M'_2| = 1$.
	Dilate $M'$ to $M''$ in such a way that $M'_1$ and $M'_2$ turn into $M''_1$ and $M''_2$ resp.
	and $|M''_1 M''_2| = d$.
	Then ``blow up'' $M''$ to $M\in \mathfrak{M}(m,n)$ using a simplex of side length $d+1$.
	The greatest common divisor of $d$ and $d+1$ is $1$, so $M$ is prime.
\end{proof}

>>>>

A slightly stronger result can also be claimed.

@@

\begin{proof}
	We apply Construction~\ref{con:planar_set_with_minimeter_1} to obtain $M'\in \mathfrak{M}(2,n-m+2)$
	with $M'_1, M'_2 \in M'$ and $|M'_1 M'_2| = 1$.
	Dilate $M'$ to $M''$ in such a way that $M'_1$ and $M'_2$ turn into $M''_1$ and $M''_2$ resp.
	and $|M''_1 M''_2| = d$.
	Then ``blow up'' $M''$ to $M\in \mathfrak{M}(m,n)$ using a simplex of side length $d+1$.
	The greatest common divisor of $d$ and $d+1$ is $1$, so $M$ is prime.
\end{proof}
